Multilocus Genotype And Mycelial Compatability Group Assessment

### 2017-06-30 doc/RMD/mlg-mcg.Rmd
remove title from S2 graph

the_communities <- data_frame(vertex = lay2$name, community = lay2$community) %>%
  mutate(comm = case_when(
    .$community == 7 ~ "A",
    .$community == 5 ~ "B",
    .$community == 1 ~ "C",
    TRUE ~ as.character(.$community)
  )) %>%
  group_by(community) %>%
  mutate(comm = ifelse(n() > 10, paste("Community", comm), "Other Communities (n < 10)")) %>%
  mutate(comm = comm) # It just so happens that the communities are in order by size.
lay2$community <- the_communities$comm
mcg_mlg_graph <- ggraph(lay2) +
  geom_node_circle(aes(r = size, lty = type, fill = community)) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native"), 
                     width = weight),
                 arrow = arrow(length = unit(0.01, "native"))) +
  geom_node_text(aes(label = gsub("MLG.", "", name), 
                     color = community, 
                     size = size/10), 
                 show.legend = FALSE) +
  coord_fixed() +
  scale_linetype_manual(values = c(1, 3)) +
  scale_edge_width(range = c(0.25, 1.5)) +
  scale_color_manual(values = c("black", "black", "white", "white")) +
  scale_fill_viridis(direction = -1, discrete = TRUE) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "bottom", legend.direction = "vertical") +
  ggtitle("Relation of Multilocus Genotypes and MCGs")

>>>>

the_communities <- data_frame(vertex = lay2$name, community = lay2$community) %>%
  mutate(comm = case_when(
    .$community == 7 ~ "A",
    .$community == 5 ~ "B",
    .$community == 1 ~ "C",
    TRUE ~ as.character(.$community)
  )) %>%
  group_by(community) %>%
  mutate(comm = ifelse(n() > 10, paste("Community", comm), "Other Communities (n < 10)")) %>%
  mutate(comm = comm) # It just so happens that the communities are in order by size.
lay2$community <- the_communities$comm
mcg_mlg_graph <- ggraph(lay2) +
  geom_node_circle(aes(r = size, lty = type, fill = community)) +
  geom_edge_link(aes(start_cap = circle(node1.size, unit = "native"), 
                     end_cap = circle(node2.size, unit = "native"), 
                     width = weight),
                 arrow = arrow(length = unit(0.01, "native"))) +
  geom_node_text(aes(label = gsub("MLG.", "", name), 
                     color = community, 
                     size = size/10), 
                 show.legend = FALSE) +
  coord_fixed() +
  scale_linetype_manual(values = c(1, 3)) +
  scale_edge_width(range = c(0.25, 1.5)) +
  scale_color_manual(values = c("black", "black", "white", "white")) +
  scale_fill_viridis(direction = -1, discrete = TRUE) +
  theme_graph(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "bottom", legend.direction = "vertical")
  # ggtitle("Relation of Multilocus Genotypes and MCGs")
